\large{Vipassana for Hackers} \\ \Huge{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-10-06 paper-two/paper-two.tex
spelling mistake
mentioning approximate locations of brain activity in diagrams

\title{%
  \Huge{Vipassana for Hackers} \\
  \large{Paper Two: The Brain} \\
  \large\textit{Version 0.2}
}
\author{Preethi Govindarajan}
\email[Correspondence email address: ]{preethi@deobald.ca}
\affiliation{Siggu.org}
\date{\today}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/top-dmn.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/side-dmn.png}
  \end{subfigure}
  \caption{Highlighted: areas of the brain firing when the Default Mode Network is active.}
  \label{fig:dmn}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/top-cen.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/side-cen.png}
  \end{subfigure}
  \caption{Highlighted: areas of the brain firing when the Central Executive Network is active.}
  \label{fig:cen}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/side-somatosensory.png}
  \caption{Location of the Sensory Homunculus.}
  \label{fig:side-somatosensory}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/top-sn.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/side-sn.png}
  \end{subfigure}
  \caption{Highlighted: areas of the brain firing when the Salience Network is active.}
  \label{fig:sn}
\end{figure}

>>>>

\title{%
  \large{Vipassana for Hackers} \\
  \Huge{Paper Two: The Brain} \\
  \large\textit{Version 0.2}
}
\author{Preethi Govindarajan}
\email[Correspondence email address: ]{preethi@deobald.ca}
\affiliation{Siggu.org}
\date{\today}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/top-dmn.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/side-dmn.png}
  \end{subfigure}
  \caption{Highlighted: approximate locations of brain regions firing when the Default Mode Network is active.}
  \label{fig:dmn}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/top-cen.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/side-cen.png}
  \end{subfigure}
  \caption{Highlighted: approximate locations of brain regions firing when the Central Executive Network is active.}
  \label{fig:cen}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=5cm]{images/side-somatosensory.png}
  \caption{Location of the Somatosensory Cortex.}
  \label{fig:side-somatosensory}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/top-sn.png}
  \end{subfigure}
  \begin{subfigure}[b]{0.48\linewidth}
    \includegraphics[width=\linewidth]{images/side-sn.png}
  \end{subfigure}
  \caption{Highlighted: approximate locations of brain regions firing when the Salience Network is active.}
  \label{fig:sn}
\end{figure}
